Simulation Study: Null Settings

### 2018-03-30 datasets/simulations/simulations-null.Rmd
Remove redundant plot in sims
Fix rchisq_2pvaluer to rchisq_pvaluer, 1-sided pval

plotsim_average(resdf, met="FDR", filter_set = excludeSet,
                merge_ihw = TRUE, errorBars = TRUE)

@@

```{r chisq4-parameters}
tstat_dist <- rchisq_perturber(4)  # functional: sampling dist/noise for test stats
null_dist <- rchisq_2pvaluer(4)    # functional: dist to calc p-values
seed <- 1023
```

>>>>

@@

```{r chisq4-parameters}
tstat_dist <- rchisq_perturber(4)  # functional: sampling dist/noise for test stats
null_dist <- rchisq_pvaluer(4)     # functional: dist to calc p-values
seed <- 1023
```
